\subsection{Operation in Fail-States}
\label{sec:failurestate}

When a fault is detected, the component would be taken offline.
This removes it from the generated State Space, and means the controller has to adapt to stabilise the dynamics of the plant.

Should a generation-side component fail, the grid is at risk of not having enough energy and frequency dropping to dangerous levels.
For this reason, the SOFCs and Turbine are paralleised, such that a single turbine \emph{can be taken offline}, as more are able to step in and ensure operation.

Should all of one type of generation-side component fail, for example the SOFC, the turbine will have to make up all the load deficit.
The turbine was not designed to have integral action, so there will be a proportional frequency error if another controller doesn't introduce integral action.
Therefore failure detection should be used (through a Kalman filter as suggested by \cite{power:kalman}) which will trigger the action of an integrator on the turbine.

Should a single electrolyser fail the remainder of active cells will consume the required amount of energy to sustain correct frequency.
Should all the electrolyser units fail, the plant will have to dump power from the grid to prevent the frequency rising and damaging domestic equipment.
This can be achieved by a \emph{load bank} which is nothing more than an array of actively cooled resistors.
Such systems are avaliable for purchase and an example found can continuously dissapate 1MW \cite{power:rdump}.

Since simulations found a maximum net power on the grid of 250MW, 300 such resistive load dumps would be needed (safey factor of 1.2). 
The control signal from the electrolyser can be redirected to the load dumps, as they have a comparable response time.

Should a catastrophic failure occur causing the plant to not keep up with demand, \emph{load shedding} will happen, which is a protective method to keep some of the grid alive and prevent a \emph{black start}. This is discussed in more detail in section \ref{sec:challengespwr}.
