\documentclass[11pt, oneside]{article}  

\usepackage{style-3yp} %this is the .sty file
\usepackage{pdflscape}
\lfoot{Enzia Schnyder} %your name in the footer

%table
\usepackage{array}
\newcolumntype{L}{>{\centering\arraybackslash}m{2.5cm}}
\newcolumntype{J}{>{\centering\arraybackslash}m{2.8cm}}

\begin{document}
\section{Sustainability}

A principal design target for the storage plant was that it must be sustainable. The plant impacts assessed in this section aim to judge if the plant:
\\ \textbf{Has a minimal environmental impact} - this includes low resource consumption, waste, pollutant emission and greenhouse gas emissions.
\\ \textbf{Has an overall positive social impact} - the social value of the plant must exceed the cost.

Issues associated with each design component are covered in their respective sections. This section will summarise these issues and include additional issues associated with the entire plant.

The plant will allow the whole of Maui to switch to a constant source of renewable energy, which currently make up only 24.8\% of Maui's energy \cite{website:mauielectric}. This would reduce lifecycle GHG emissions by up to 700 tonnes $CO2e/GWh$ \cite{GHG}. The only direct greenhouse gas emissions from the ESS plant are small amounts of $NO_x$ from the gas turbine, which will only run 5\% of the time and indirect emissions from transport and construction of the plant. The waste products of the plant are pure oxygen, nitrogen and water which are not polluting gases. There is also a small amount of $CO_2$ that comes from the air separator but this comes from the air taken in so does not add net $CO_2$ to the atmosphere. The main inputs are air and seawater, which are abundant in the plant location. Therefore, the plant represents a large improvement to Maui's current environmental impact.

The construction and operation of the plant will require significant manpower, creating jobs and boosting the local economy of Maui. Residents will also benefit from gaining full access to clean energy and it allows the island to reach its renewable energy target of 100\% by 2045 \cite{website:hcei}. Although there will be minor visual and noise pollution, there will still be an overall positive societal impact.

%\printbibliography[heading=subbibliography]
\bibliography{Sustainability}
\bibliographystyle{unsrt}
\end{document}