\documentclass[11pt,oneside]{article}
\usepackage{style-3yp}
\lfoot{Lai Chong}
\let\subsubsubsection\paragraph


\begin{document}
\singlespacing
\setlength{\parindent}{0pt}
\section{Intro}
    \begin{enumerate}
        \item Name
        \item Separation of air by cryogenic distillation
    \end{enumerate}

\section{Slide 1}
    Main objective:
    \begin{enumerate}
        \item Produce high purity N2
        \item Sustain Haber-Bosch
        \item Process 97 thousand tpy of air
    \end{enumerate}
    Here are the design requirements, will talk more in conclusion section.

\section{Slide 2}
    Lower pressure = low boiling point but higher volatility. \\
    Find balance between duty and separation.

\section{Slide 3}
    Schematic for cryogenic plant. \\
    Key features:
    \begin{enumerate}
        \item Air filtering
        \item Liquefaction unit
        \item Double-column system
    \end{enumerate}

\section{Slide 4 + 5}
    Process:
    \begin{enumerate}
        \item Compression 5.6 to 50
        \item Cooling using LPC cold stream
        \item Expansion 50 to 5.6
        \item Separation and recycling
    \end{enumerate}
    66\% of inlet liquefied.
    
\section{Slide 6}
    Key features:
    \begin{enumerate}
        \item D and B of HPC are fed to LPC
        \item Rc1 connected to Rb2
    \end{enumerate}

\section{Slide 7}
    Initial model:
    \begin{enumerate}
        \item Rigorous separation in HPC
        \item Further purification in LPC
        \item total 64 stages
        \item LPC total reflux due to large liquid stream from HPC D
        \item Not ideal
    \end{enumerate}
    
\section{Slide 8 + 9}
    Optimisation on:
    \begin{enumerate}
        \item HPC output
        \item Reflux, focus on
    \end{enumerate}
    Larger reflux
    \begin{enumerate}
        \item more effective separation at each stage
        \item less stages required
        \item shorter column
        \item but higher heat duty
    \end{enumerate}
    Links to:
    \begin{enumerate}
        \item fixed column cost
        \item cooling/heating duty
    \end{enumerate}
    Hence do a cost analysis: optimum at 1.75.

\section{Slide 10}
    Final model:
    \begin{enumerate}
        \item Slight separation in HPC, equimolar flow out top and bottom
        \item Purification in LPC
        \item total 37 stages
    \end{enumerate}
    
\section{Slide 11}
    Outlet
    \begin{enumerate}
        \item 74 thousand tpy of N2 at req. purity
        \item 23 thousand tpy of O2 at high purity
        \item 44 tpy dry ice
    \end{enumerate}
    
\section{Slide 12}
    Design requirement:
    \begin{enumerate}
        \item Meet criteria set by project
        \item Utilised internal heat transfer w/o external duty, i.e. self-sufficient
        \item Natural raw material and no harmful byproducts, i.e. sustainable
        \item Safety and risk aspects are analysed in a HAZOP study
        \item Cost-effective as proven in the team analysis
    \end{enumerate}
    Meets Objective and Requirements, therefore success.
\end{document}